Normalization by Evaluation for Sized Dependent Types

### 2017-06-12 nbe/icfp17.tex
Typos

Fig.~\ref{fig:judge} lists the inductive and derived judgements of our type theory and
figures~\ref{fig:ty} and \ref{fig:eq} the inference rules.
We have \fbox{boxed} the rules dealing with irrelevant size application.
Fig.~\ref{fig:nat} add the typing and equality rules for case distinction
and recursion on natural numbers.
Judgement $\Gamma \der T : \Adm \ell$ characterizes the valid type
annotations $T$ in recursion $\fix[\ell] T t$.  The type constructor $T$
has to be monotone in the size argument; this is a technical condition
for type-based termination \cite{gimenez:typeBased}.  We will make use
of it in Section~\ref{sec:comp}.
We write \fbox{$\DD :: J$} to express that $\DD$ is a derivation of judgement $J$.

@@

\begin{lemma}[$\NAT$ is cocontinuous]
  \label{lem:limit}
  $\NAT(\infty) = \bigcup_{\alpha < \infty} \NAT(\alpha)$.
\end{lemma}
\begin{proof}
  By induction on $a = a' \in \NAT(\infty)$, we can easily show $a = a' \in \NAT(\alpha)$ for some $\alpha < \infty$.
  For instance, $\alpha$ could be number of uses of the successor rule plus one.
\end{proof}

@@

In the long run, we wish for a type-directed equality check that does
not normalization in one go, but interleaves weak head normalization
with structural comparison.
Such a equality test is at the heart of Agda's type
checker and it generates constraints for meta variables
involved in type reconstruction \cite{norell:PhD}.  However, the usual
bidirectional construction \cite{abelScherer:types10} does not seem to
go through as we lack uniqueness of types (and even principal types).

>>>>

Fig.~\ref{fig:judge} lists the inductive and derived judgements of our type theory and
figures~\ref{fig:ty} and \ref{fig:eq} the inference rules.
We have \fbox{boxed} the rules dealing with irrelevant size application.
Fig.~\ref{fig:nat} adds the typing and equality rules for case distinction
and recursion on natural numbers.
Judgement $\Gamma \der T : \Adm \ell$ characterizes the valid type
annotations $T$ in recursion $\fix[\ell] T t$.  The type constructor $T$
has to be monotone in the size argument; this is a technical condition
for type-based termination \cite{gimenez:typeBased}.  We will make use
of it in Section~\ref{sec:comp}.
We write \fbox{$\DD :: J$} to express that $\DD$ is a derivation of judgement $J$.

@@

\begin{lemma}[$\NAT$ is cocontinuous]
  \label{lem:limit}
  $\NAT(\infty) = \bigcup_{\alpha < \infty} \NAT(\alpha)$.
\end{lemma}
\begin{proof}
  By induction on $a = a' \in \NAT(\infty)$, we can easily show $a = a' \in \NAT(\alpha)$ for some $\alpha < \infty$.
  For instance, $\alpha$ could be the number of uses of the successor rule plus one.
\end{proof}

@@

In the long run, we wish for a type-directed equality check that does
not do normalization in one go, but interleaves weak head normalization
with structural comparison.
Such an equality test is at the heart of Agda's type
checker and it generates constraints for meta variables
involved in type reconstruction \cite{norell:PhD}.  However, the usual
bidirectional construction \cite{abelScherer:types10} does not seem to
go through as we lack uniqueness of types (and even principal types).
